## Scores as a function of time / trial :
***

### Linear fit on time/trials:

```{r}
data.long.time.G <- data.long %>% 
  group_by(subject, mode) %>% 
  mutate(id = seq_along(hotspot)) %>% 
  ungroup() %>%
  select(id, everything()) %>%
  filter(mode == "G") %T>% print
```

```{r}
lin.mod.time <- lm(time ~ id, data.long.time.G)
```

```{r}
broom::tidy(lin.mod.time) %>%
  DT::datatable(
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: LM time model summary')
  )
) %>% formatRound(2:5, 4)
```


```{r}
fig <- data.long.time.G %>% 
  ggplot(aes(x = id, y = time, color = subject)) +
  labs(title= glue('Fig {tc<-tc+1}: Score evolution per trial (guided mode)'), x = "Trials") +
  theme(legend.position = "none") +
  facet_wrap(. ~ subject, ncol = 2) +
  geom_point() +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    #family = gaussian(link = 'log'),
    alpha = .15,
    aes(fill = subject)
  )

ggplotly(fig)
```

#### (TODO) Fit metrics:

[!] TODO: fit per subject --> random effect on subject ?

```{r}
broom::glance(lin.mod.time) %>% 
  DT::datatable(
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Linear model evaluation summary')
  )
) %>% formatRound(1:10, 4)
```


Overall, there's a very bad linear fit on trials/time with current data. We'd need more values see an eventual temporal trend in the data, with the high amount of variations in scores per hotspot & per subject.

### (TODO) Linear fit with autocorrelation:

[!] TODO: see [here](https://www.r-bloggers.com/linear-regression-with-correlated-data/)

```{r}
#lin.mod.time.ar <- nlme::gls(time ~ mode, correlation=nlme::corAR1(form=~1), data = data.long.time.G)
#anova(lin.mod.time, lin.mod.time.ar)
```

### Exponential fit on time/trials:

No convergence with current data

```{r}
# Estimating the initial parameters (using a linear model)
# TODO: check nlstools

##exp.forumla <- alpha * exp(beta * x) + theta

# theta.0 <- min(dt_time$time) * 0.5
# 
# model.0 <- lm(log(time - theta.0) ~ id, data=dt_time)  
# alpha.0 <- exp(coef(model.0)[[1]])
# beta.0 <- coef(model.0)[[2]]
# 
# start <- c(alpha = alpha.0, beta = beta.0, theta = theta.0)
# print(start)
```

```{r}
# fig <- ggplot(data_P1, aes(x = id)) +
#   labs(title= glue('Fig {tc<-tc+1}: Test'), x = "Trials") +
#   geom_point(aes(y = time)) +
#   stat_function(fun = function(x) start[1] * exp(start[2] * x) + start[3], n = 100, color="red")
# 
# ggplotly(fig)
```

```{r}
# exp.model <- nlme::gnls(time ~ alpha * exp(beta * id) + theta, data=data_P1, start=start)
# exp.model
```

### Sigmoid fit on time/trials:

No convergence with current data
```{r}
# sig.mod <- gnls(time ~ SSlogis(id, asym, xmid, scal), data=data_P1, start=list(a=1,b=.5,c=25))
# summary(sig.mod)
```

```{r}
# fig <- ggplot(data_P1, aes(x = id)) +
#   labs(title= glue('Fig {tc<-tc+1}: Sigmoid fit'), x = "Trials") +
#   geom_point(aes(y = time)) +
#   stat_function(fun = function(x) params[1] / (1 + exp(-params[2] * (x - params[3]))), n = 100, color="blue")
# 
# ggplotly(fig)
```

Both sigmoid & exponential fit don't converge with the current data.

## Pairwise differences evaluation:
***

### Pairwise differences summary :

Paired by hotspot

```{r}
pairwise <- data.long %>%
  group_by(subject, hotspot) %>%
  summarize(diff = abs(diff(time))) %>%
  ungroup() %T>% print
```

```{r}
DT::datatable(
  pairwise,
  class = 'cell-border stripe compact',
  caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;',
                                    glue('Fig {tc<-tc+1}: Summary statistics of pairwise differences'))
)
```

### Pairwise differences distribution :

```{r}
pairwise.fig <- pairwise %>%
  ggplot(aes(x=diff)) +
  geom_histogram(aes(y=..density..), binwidth=5, alpha=0.9, color="blue", fill="blue", boundary = 1) +
  geom_density(alpha=0.6, adjust=1.2, color="blue", fill="blue") + 
  labs(title= glue('Fig {tc<-tc+1}: Distribution of pairwise score differences'), x = "Pairwise difference in time to find the hotspot")

ggplotly(pairwise.fig)
```

#### Violin + Box-plot:

```{r}
plot_ly(
    pairwise,
    y = ~diff,
    type = 'violin',
    points = 'all',
    box = list(visible = T),
    meanline = list(visible = T),
    colors = "Set1"
  ) %>%
  layout(
    yaxis = list(title = "Pairwise time difference", range=c(0,120)),
    title = glue('Fig {tc<-tc+1}: Violin + Box-Plots of pairwise differences')
  )
```

### Pairwise differences normality:

#### QQ Plot:

```{r}
ggplotly(
  ggplot(pairwise, aes(sample = diff)) + 
    geom_qq(color="blue") + 
    geom_qq_line() +
    labs(title= glue('Fig {tc<-tc+1}: QQ plot of score diffrences'))
  )
```

#### Summary:

```{r}
moments <- pairwise %>%
  summarize(
    n = n(),
    median = median(diff),
    mean = mean(diff),
    skew = skewness(diff),
    kurt = kurtosis(diff),
    SW.p = shapiro.test(diff)$p.value
  )
  
DT::datatable(
  moments,
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Summary statistics of score differences')
  )
) %>%
  formatRound(4:ncol(moments), 4) %>%
  formatStyle('SW.p',
              color = styleInterval(alpha, c('red', 'gray')),
              fontWeight = styleInterval(alpha, c('bold', 'normal')))
```


### Box-Cox transformation:

Box-Cox transform with $\lambda = 6$

```{r}
pairwise.boxcox <- pairwise %>%
  mutate(bc.diff = BoxCox(diff, 6))
```

```{r}
pairwise.boxcox.fig <- pairwise.boxcox %>%
  ggplot(aes(x=bc.diff)) +
  geom_density(alpha=0.8, color="blue", fill="blue", adjust=1.2) +
  labs(title= glue('Fig {tc<-tc+1}: Pairwise score difference distribution (Box-Cox)'), x = "BoxCox(Time to find hotspot)")

ggplotly(pairwise.boxcox.fig)
```

```{r}
ggplotly(
  ggplot(pairwise.boxcox, aes(sample = bc.diff)) + 
    geom_qq(color="blue") + 
    geom_qq_line() +
    labs(title= glue('Fig {tc<-tc+1}: QQ plot of Box-Cox corrected score diffrences'))
  )
```

```{r}
summary.pairwise.boxcox <- pairwise.boxcox %>%
  summarize(
    n = n(),
    skew = skewness(diff),
    kurt = kurtosis(diff),
    SW.p = shapiro.test(diff)$p.value,
    skew.boxcox = skewness(bc.diff),
    kurt.boxcox = kurtosis(bc.diff),
    SW.p.boxcox = shapiro.test(bc.diff)$p.value
  )

DT::datatable(
  summary.pairwise.boxcox,
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Summary statistics of Box-Cox transformed score differences')
  )
) %>%
  formatRound(2:ncol(summary.pairwise.boxcox), 4) %>%
  formatStyle(c('SW.p', 'SW.p.boxcox'),
              color = styleInterval(alpha, c('red', 'gray')),
              fontWeight = styleInterval(alpha, c('bold', 'normal')))
```

The Box-Cox transform seems to make the date more normal --> to investigate ?

## Non-parametric comparaisons:
***

### Wilcoxon Signed-Rank Test:

```{r}
data.wide.GN <- data.long %>% reshape2::dcast(subject+hotspot~mode,  value.var="time") %T>% print
#print(data.wide.GN)
```

```{r}
wilcoxon.res <- wilcox.test(data.wide.GN$N, data.wide.GN$G, paired=TRUE, conf.int=TRUE, correct = FALSE)

wilcoxonZ(
  data.wide.GN$N,
  data.wide.GN$G,
  mu = 0,
  paired = TRUE,
  exact = FALSE,
  correct = FALSE,
  digits = 3
)

wilcoxon.res %>% tidy
```
```{r}
median(data.wide.GN$G)
median(data.wide.GN$N)
```


#### Effect size:

```{r}
wilcoxon.es <- wilcoxon.res$statistic / sqrt(nrow(data.wide.GN))
#wilcoxon.es2 <- data.long %>% rstatix::wilcox_effsize(time ~ mode, paired=TRUE)
print(wilcoxon.es)
```

Effect-size for Wilcoxon Signed-Rank Test is `r wilcoxon.es`

### (TODO) Resampling test:

[!] TODO

## Parametric models :
***

### LM model:

I'm only fitting a linear model for experimenting: with the current data, almost every assumption of Linear Models is violated.

```{r results=F}
lin.mod <- lm(time ~ mode, data.long)
```

#### Heteroscedasticity:

```{r}
par(mfrow=c(2,2))
plot(lin.mod, 1:2)
```

* Residual vs Fitted: The difference in spread in both conditions points towards heteroscedasticity, so that linear model doesn't hold.
* QQ plot: data is also obviously not normal.

##### Heteroscedasticity test :

```{r}
lmtest::bptest(lin.mod) %>% tidy
```

No surprise on the heteroscedasticity with the right-censoring of the measures.

[!] TODO: try to fix it ?  
- Data transform (Box-Cox, ...) ?   
- GLS Regression ?  
- Truncated regression ?

#### Predicted values: 

```{r}
ggpredict(lin.mod, terms = c("mode")) %>% plot(add.data = TRUE)
```

#### Model fit:

```{r}
broom::glance(lin.mod)
```
Significant effect of the guidance mode (but we can't really use that test/model)

AIC of ~747

#### Effects / contrasts :

```{r}
#broom::tidy(car::Anova(lin.mod))
```

```{r}
broom::tidy(lin.mod) %>%
  DT::datatable(
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: LM model summary')
  )
) %>% formatRound(2:5, 4)
```

```{r}
emm1 = emmeans(lin.mod, specs = pairwise ~ mode, adjust = "none", type = "response")

emm1$contrasts %>% 
  summary(infer = TRUE) %>% 
  as.data.frame %>%
  DT::datatable(
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: LM contrast summary')
  )
) %>% formatRound(c(3,5,6,7,8), 4)
```

[!] TODO: bootstrap CI measures ?

```{r}
plot(emm1) + 
  theme_bw() + 
  labs(x = "Estimated time (mean, 95CI)", y = "Condition")
```





### (TODO) GLM model:

[!] TODO: find the optimal familly and link function for the data.

```{r}
glin.mod <- glm(time ~ mode, data.long, family=Gamma(link="log"))
```

```{r}
par(mfrow=c(2,2))
plot(glin.mod, 1:2)
```

#### Model fit:

```{r}
broom::glance(glin.mod) %>% 
  DT::datatable(
  class = 'cell-border stripe compact',
  options = list(autoWidth = TRUE),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: GLM evaluation summary')
  )
) %>% formatRound(1:10, 4)
```





### (TODO) GLMM model:

[!] TODO

```{r}
data.long.time2 <- data.long %>% 
  group_by(subject, mode) %>% 
  mutate(id = seq_along(hotspot)) %>% 
  ungroup() %>%
  select(id, everything()) %T>% print
```

```{r}
glmm1 <- lmer(time ~mode + (1|subject), data=data.long.time2)
glmm1
```

Checking model assumptions (normality of residuals = homeoscedasticity along predicted values)
```{r}
par(mfrow=c(2,2))
plot(glmm1)
```

### Model comparison:

```{r}
t1 <- tbl_regression(lin.mod)
t2 <- tbl_regression(glin.mod, exponentiate = TRUE)

tbl_merge(
    tbls = list(t1, t2),
    tab_spanner = c("**Linear**", "**Generalized (Gaussian, Log link)**")
  ) %>%
  bold_labels()
```



[!] TODO: model fit comparison

```{r}
# adj_R2 <-rbind("exp.model" = summary(exp.model)$adj.r.squared,
#                "sig.model" = summary(sig.model)$adj.r.squared,
#                "lin.model" = summary(lin.model)$adj.r.squared)
# 
# colnames(adj_R2) <- "adj_R2"
# adj_R2
```